RationalGRL: A Framework for Argumentation and Goal Modeling

### 2019-02-03 main.tex
main

\title{RationalGRL: A Framework for Argumentation and Goal Modeling}
\author{Marc van Zee  \and Floris J. Bex\and Sepideh Ghanavati}
\institute{Marc van Zee \at Google BRAIN, Z\"urich, Switzerland \\\email{marcvanzee@gmail.com} 
\and Floris Bex \at Department of Information and Computing Sciences, Utrecht University, Utrecht, The Netherlands 
				\at Tilburg Institute for Law, Technology, and Society, Tilburg University, Tilburg, The Netherlands \\\email{f.j.bex@uu.nl}
\and Sepideh Ghanavati \at Department of Computer Science, Texas Tech University, Lubbock TX, USA \\\email{sepideh.ghanavati@ttu.edu} }

>>>>

\title{RationalGRL: A Framework for Argumentation and Goal Modeling}
\author{Authors names anonymized for review}
